Synthesizing Symmetric Lenses

### 2018-07-11 papers/SymmetricLenses/main.tex
respond to steve comments

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \saz{BS isn't in the figure}\BSOpt{} is the full bijective lens synthesis algorithm. \SSNCOpt{} is the
    symmetric synthesis algorithm without using a library of existing lenses.
    \saz{BSNC isn't in the figure}\BSNCOpt{} is the bijective synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete a majority of the benchmarks without using compositional
    synthesis.}
  \label{fig:times}
\end{figure}

For each benchmark in our benchmark suite, we ran every mode on it with a
timeout of 30 seconds, and averaged the result over 5 runs.
Figure~\ref{fig:times} summarizes the results of these tests. We find that our
algorithm is able to synthesize all of the benchmarks in our benchmark suite in
under 30 seconds. Without compositional synthesis, the synthesis algorithm is
able to solve 26 problem instances. Recall from
Section~\ref{subsec:optimizations} that users may tune the termination
metric. Success on this set of benchmarks requires we tune that termination
codition (e.g. for some benchmarks, allowing the system flexibility to spend
more time considering more of the search space). In
Section~\ref{subsec:effect-of-heuristics}, we will consider the effect of fixing
the termination metric. \saz{If there's space: Maybe say something about how hard it was to tune?}

>>>>

\begin{figure}
  \includegraphics{generated-graphs/times}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \SSNCOpt{} is the symmetric synthesis algorithm without using a library of
    existing lenses. Our symmetric synthesis algorithm is able to complete all
    benchmarks in our benchmark suite in under 30 seconds, and is able to
    complete a majority of the benchmarks without using compositional
    synthesis.}
  \label{fig:times}
\end{figure}

For each benchmark in our benchmark suite, we ran every mode on it with a
timeout of 30 seconds, and averaged the result over 5 runs.
Figure~\ref{fig:times} summarizes the results of these tests. We find that our
algorithm is able to synthesize all of the benchmarks in our benchmark suite in
under 30 seconds. Without compositional synthesis, the synthesis algorithm is
able to solve 26 problem instances. Recall from
Section~\ref{subsec:optimizations} that users may tune the termination metric.
Success on this set of benchmarks requires we tune that termination codition
(e.g. for some benchmarks, allowing the system flexibility to spend more time
considering more of the search space). In
Section~\ref{subsec:effect-of-heuristics}, we will consider the effect of fixing
the termination metric. In practice, we found customizing the termination metric
to be quite easy: if manual inspection of the lens showed there were too few
bijections, we would increase the termination parameter. If synthesis took too
long, we would decrease it.
